%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {Senior Backend Engineer} % Job title
    {HTC Vive / Viveport} % Organization
    {New Taipei City, Taiwan} % Location
    {Sep. 2020 - Now} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {Implement Y to accomplish X to achieve Z} e.g. 透過實作分散式快取減少物件 render time 50% 從而達到減少 10% 登入時間
        \item {Designed and implemented a distributed audio recording system for the metaverse platform to record and store audio data from multiple sources. }
        \item {Designed and implemented user accounts management service by integrating APIs with a cloud hosting third-party service as a part of the multi-platform SaaS product to standardize the way of user accounts management amongst different projects and mitigating code duplicity.}
        \item {Recommend, introduce and migrate to a high-performance asynchronous web framework to reduce 85\% micro-services API response time.}
        \item {Participating in building and deploying overall service infrastructure utilizing Docker container, CDN, and several AWS stacks (including EC2, EKS, MongoDB, RDS, Route 53, S3, Lambda, and CloudWatch), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {Designed and implemented the 99.99\% up-time RESTful APIs for the critical multi-platform application with over 90\% unit test coverage, which provided a critical connectivity channel for distributed functionality and kept manageable code complexity with micro-services architecture.}
            %\item {Provisioned an easily managable hybrid infrastructure(Amazon AWS + On-premise) utilizing IaC(Infrastructure as Code) tools like Ansible, Packer and Terraform.}
            %\item {Built fully automated CI/CD pipelines on CircleCI for containerized applications using Docker, AWS ECR and Rancher.}
            %\item {Implemented several API microservices in Node.js Koa and in the serverless AWS Lambda functions.}
            %\item {Deployed a centralized logging environment(ELK, Filebeat, CloudWatch, S3) which gather log data from docker containers and AWS resources.}
            %\item {Deployed a centralized monitoring environment(Grafana, InfluxDB, CollectD) which gather system metrics as well as docker run-time metrics.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Senior Software Engineer} % Job title
    {InfoBoom Ltd.} % Organization
    {New Taipie City, Taiwan} % Location
    {Feb. 2020 - Sep. 2020} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for refactoring the existing WebRTC server infrastructure from monolithic to microservice to improve scalability and reduce cost.}
        \item {Responsible for the improvement of the core cryptography library of the instant messaging SaaS product with a higher security level to be fully ISO27001 compliant and Taiwan MAS compliant.}
        \item {Recommended, introduced and built fully automated CI/CD pipelines on GitLab for the business-critical multi-platform cryptography library using Docker, resulting in a 3x reduction of average deployment time.}
            %\item {Implemented RESTful API server for car rental booking application(CARPLAT in Google Play).}
            %\item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Korea.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Product Developer} % Job title
    {Synology} % Organization
    {Taipei, Taiwan} % Location
    {Dec. 2016 - Jun. 2018} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed new features for the mail server application in C/C++. Resulting in 10+ releases delivered just in time.}
        \item {Designed and developed new features for the mail server application to be GDPR compliant and data privacy compliance.}
        \item {Coordinated with engineering and product teams in the identification of customer requirements and development of new features for the mail server application.}
            %\item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
            %\item {Implemented a distributed web stress test tool with high anonymity.}
            %\item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry
    {Research Assistant} % Job title
    {National Taiwan University} % Organization
    {Taipei, Taiwan} % Location
    {May. 2014 - Aug. 2014} % Date(s)
    {}

    %---------------------------------------------------------
\end{cventries}
